---
title: "Network Analysis"
author: "Linus Covic"
date: "18 3 2022"
output:
  word_document: default
  pdf_document: default
---

```{r, echo=F, message=FALSE, warning=FALSE, results='hide'}
library(network)
library(igraph)
library(dplyr)
library(sna)
library(dplyr)
library(gmodels)
library(rcompanion)
library(ggplot2)
library(ggraph)
library(movienetdata) 
library(devtools) 
library(tidyr)
library(formattable)
library(intergraph)
library(knitr)

# Set working director
setwd("C:/Users/linus/OneDrive/Uni/Master/Social Theory/Assignement Social Networks")
```


# PART A 
## Klubbdata 
```{r, message=FALSE, warning=FALSE, results='hide'}
# Load Klubb-Data
edges <- read.csv("klubbdata_edges.csv")
nodes <- read.csv("klubbdata_nodes.csv")

klubb_graph <- graph.data.frame(d =edges, vertices = nodes, directed = F)
adj_mat <- as.matrix(get.adjacency(klubb_graph))

klubb_net <- network(edges, vertices = nodes, directed = F)
```


### 1. Is the network directed or undirected? 
```{r, message=FALSE, warning=FALSE}
sum(edges$source < edges$target) == nrow(edges)
```
This shows the source is always lower then the target, which is a strong indication for the network beeing undirected, as there is no tie that is going in both direction. 
Therefore, the network is considered as undirected in the following analysis. 


### 2. How many actors and ties there are? 
```{r, message=FALSE, warning=FALSE}
# Number of nodes 
network.size(klubb_net)

# Number of edges
network.edgecount(klubb_net)
```
The network has 34 nodes and 78 edges.

### 3. What is the density of the network? 
```{r, message=FALSE, warning=FALSE}
gden(klubb_net, mode="graph")
```
The density of the network is 0.139.

### 4. What is the average degree of the network? 
```{r, message=FALSE, warning=FALSE}
sum(degree(klubb_net)/2)/nrow(nodes)
```
The average degree for the network is 4.588.

### 5. What is the average shortest path of the network? 
```{r, message=FALSE, warning=FALSE}
average.path.length(klubb_graph, directed = F)
```
The average shortest path of the network is 2.408.

### 6. Who are the 2 most central characters in this network?
```{r, message=FALSE, warning=FALSE}
# Specify degree and betweenness 
degrees <- as.factor(degree(klubb_net)/2)
betweenness <- betweenness(klubb_net, gmode="graph", cmode="undirected")
degrees <- as.data.frame(cbind(nodes$ID, degrees, betweenness))
  
degrees <- degrees %>%
  arrange(desc(degrees))
head(degrees, 2)

degrees <- degrees %>%
  arrange(desc(betweenness))
head(degrees, 2)
```
It shows that node 34 and 1 are the most central actors both in term of 
degrees and betweenness. However, while node 34 has a higher number of degrees: 11 compared to 10 for node 1, node 1 has a higher betweenness with 231 compared to 161 for node 34.  


### 7. Are there different communities in the network (use Louvain algorithm)? Describe and visualise the results. Report correlation with actual club membership. 
```{r, message=FALSE, warning=FALSE}
# Get Louvain membership scores 
louvain <- cluster_louvain(klubb_graph)
membership <- as.factor(membership(louvain))


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Create Plot
g <- ggraph(klubb_net, layout="fr")+
  geom_edge_link(edge_colour="grey") +
  geom_node_point(
    aes(color = membership,
        size = degrees$degrees)
  ) +
  theme_graph()+
  labs(color="Cluster", shape="Club")

g + guides(size = F)
```
The Graph shows that a clustering with the Louvain algorithm leads to four clusters within the network. 

### 8. Perform clustering based on edge betweenness (use cut-off to 2 clusters). How well do the clustering results match with the actual club membership? Report correlation and create a network visualisation that shows both to which cluster and club actors belong to. 
```{r, message=FALSE, warning=FALSE}
# Get Cluster mebership
cluster <- cluster_edge_betweenness(klubb_graph)
cluster <- as.factor(cut_at(cluster, no = 2))

nodes$cluster <- cluster 

# Create a Crosstable 
cross.tab <- CrossTable(nodes$faction, nodes$cluster, prop.chisq = F,
                        prop.r = F, prop.t = F)
# Calculate Correlation 
cramerV(cross.tab$t)

```
It shows that except for one person the edge betweeness for all actors represents the actual club membership. This is also shown by a Cramer V level of 0.942 which is very close to a perfect correlation of 1. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
g <- ggraph(klubb_net, layout="fr")+
  geom_edge_link(edge_colour="grey") +
  geom_node_point(
    aes(color = as.factor(nodes$faction),
        size = degrees$degrees,
        shape = cluster)
  ) +
  theme_graph()+
  labs(color="Club", shape="Cluster")

g + guides(size = F)
```
The same is shown by the graph. Color (representing actual club membership) and Shape (representing clustering by edge betweenness) show the same pattern except for one actor. 


## Starwars
Load Data
```{r, echo=FALSE,message=FALSE, warning=FALSE, results='hide'}
devtools::install_github("pj398/movienetdata") 
data("starwars_tfa", "movienetdata") 
data(package = "movienetdata") 
force(starwars_tfa) 
```


```{r, message=FALSE, warning=FALSE, results='hide'}
# Create network, graph, edgelist
starwars_net <- network(starwars_tfa$adjacency, directed = T) 

starwars_nodes <- starwars_tfa$node_list

starwars_adj <- starwars_tfa$adjacency

starwars_graph <- asIgraph(starwars_net)
```


### 9. Is the network directed or undirected? 
```{r, message=FALSE, warning=FALSE, results='hide'}
starwars_adj <- starwars_tfa$adjacency
rowSums(starwars_adj - t(starwars_adj))
```
Since the rowSums are not equal to 0 the Network is directed. 

### 10.  How many actors and ties there are? 
```{r, message=FALSE, warning=FALSE}
network.size(starwars_net)
network.edgecount(starwars_net)
```
There are 31 actors and 149 edges in the network.

### 11.  What is the density of the network? 
```{r, message=FALSE, warning=FALSE}
gden(starwars_net)
```
The density of the network is 0.160

### 12.  What is the average degree of the network? 
```{r, message=FALSE, warning=FALSE}
sum(degree(starwars_net))/network.size(starwars_net)
```
The average degree of the network amount to 9.613

### 13.  What is the average shortest path of the network? 
```{r, message=FALSE, warning=FALSE}
average.path.length(starwars_graph)
```
The average shortest path of the actors is 1.36.

### 14.  Who are the 3 most important characters in this movie? 
 
```{r, message=FALSE, warning=FALSE}
# Caltulating indegree, outdegree and degree
starwars.out.deg <- degree(starwars_net, cmode = "outdegree")
starwars.in.deg <- degree(starwars_net, cmode = "indegree")
starwars.degree <- degree(starwars_net, cmode = "freeman")

# Calculating betweenness
starwars_betweenness <- betweenness(starwars_net, gmode="digraph", cmode="directed")

# Calculating closeness centrality
starwars_closeness <- igraph::closeness(starwars_graph)

# Combine nodes with degree and betweenness measures 
starwars_nodes <- cbind(starwars_nodes, starwars.in.deg, starwars.out.deg, starwars.degree, starwars_betweenness, starwars_closeness)

# Get the actors with the highest measures
# Outdegree
head(arrange(starwars_nodes, desc(starwars.out.deg)),3)[,2]
# Indegree
head(arrange(starwars_nodes, desc(starwars.in.deg)),3)[,2] 
# Degree
head(arrange(starwars_nodes, desc(starwars.degree)),3)[,2]
# Betweenness
head(arrange(starwars_nodes, desc(starwars_betweenness)),3)[,2]
# Closeness 
head(arrange(starwars_nodes, desc(starwars_closeness)),3)[,2]


```
Poe Dameron, Han Solo, and Finn have the highest number of ties with other actors in the movie, both in terms of in- and out degree. Moreover they have the closest distance to all other actors (measured by the closeness centrality). Given these measures I would consider these three characters as the most important ones, even though Kylo Ren shows a quite high betweenness centrality. 



### 15.  Who does Rey interact with in the movie? 
```{r, message=FALSE, warning=FALSE}
# Ray's char_ID 
starwars_nodes$char_ID[starwars_nodes$char_name == "Rey"]

# get Ray's neighbors 
c <- get.neighborhood(starwars_net, 7)
starwars_nodes[starwars_nodes$char_ID %in% c,2]
```
Ray's network neighbors are Kylo Ren, Finn, Unkar, Han SOlo, and Maz Kanata


### 16.  Visualise the network so that node size depends on some centrality measure and node colour corresponds to the sex of the character. 
```{r, echo = F, message=FALSE, warning=FALSE}
starwars_nodes$char_female <- factor(starwars_nodes$char_female, labels = c("other", "female"))   

starwars_plot <- ggraph(starwars_net, layout="fr")+
  geom_edge_arc(edge_colour="grey") +
  geom_node_point(
    aes(color = as.factor(starwars_nodes$char_female),
        size = starwars.degree)) +
  theme_graph()+
  labs(color="Sex", size = "Degrees")

starwars_plot 

```

### 17.  Briefly compare the two networks to other real-life networks (use the examples from the last slide in Lecture 2). 

An important thing to not at the beginning is that the two inspected networks are much smaller in terms of edges and nodes than other real-life networks. This also has a strong influence on other measures as degree, density etc, which strongly limits the comparability of the networks. 

However the following table presents some key measure for the networks:
```{r, echo = F, message=FALSE, warning=FALSE}
matrix <- matrix(c(449913, 25516482, 113.43, 3.48, 
                   573, 477, 1.66, 16.01,
                   34, 78, 4.59, 2.41,
                   31, 149, 9.61, 1.36),
                 ncol = 4, byrow = T)

networks <- as.data.frame(matrix)
networks <- cbind(c(rep("Undirected",4)), networks)

colnames(networks) <- c("Directed/Undirected", "Nodes", "Edges","Mean degree", "Average shortest path")

rownames(networks) <- c("Film actors", "Student dating", "Klubb data", "Starwars")

networks
```
It shows that both the klubb-network and the Starwars network show a mean degree between the Film actor network and the Student network. This also makes sense theoretically, since the networks measure differnet types of ties. While the edges for the Student network represent a more romantic dating interaction, the other networks represent more simple interactions.
This also influencees the average shortest path which is much higher for the Student network. 


# PART B 

```{r echo=F, message=FALSE, warning=FALSE, results='hide'}
# Building the Network
g <- graph.empty(directed = FALSE)

g <- add_vertices(
  g, 
  17, 	
  name=c("Li", "So", "Bj", "Ve", "He", "Anj", "And", "Ju", "Lu", "Ch", "Mic", "Da", "Co", "Ol", "En", "Gr", "Mil")
) 

# adding edges 
g <- g + edge("Li","So")
g <- g + edge("Li","Bj")
g <- g + edge("Li","Ve")
g <- g + edge("Li","He")
g <- g + edge("Li","Da")
g <- g + edge("Li","En")

g <- g + edge("So", "Bj")
g <- g + edge("So", "Ve")
g <- g + edge("So", "He")
g <- g + edge("So", "Da")
g <- g + edge("So", "Co")
g <- g + edge("So", "Gr")

g <- g + edge("Bj", "He")
g <- g + edge("Bj", "Anj")
g <- g + edge("Bj", "Ju")

g <- g + edge("Ve", "Da")
g <- g + edge("Ve", "Co")
g <- g + edge("Ve", "En")
g <- g + edge("Ve", "Mil")
g <- g + edge("Ve", "Gr")

g <- g + edge("He", "Anj")
g <- g + edge("He", "And")
g <- g + edge("He", "Ju")
g <- g + edge("He", "Lu")
g <- g + edge("He", "Ch")
g <- g + edge("He", "Mic")

g <- g + edge("Anj", "And")
g <- g + edge("Anj", "Ju")
g <- g + edge("Anj", "Lu")
g <- g + edge("Anj", "Ch")
g <- g + edge("Anj", "Mic")

g <- g + edge("And", "Ch")
g <- g + edge("And", "Mic")

g <- g + edge("Ju", "Lu")
g <- g + edge("Ju", "Ch")
g <- g + edge("Ju", "Mic")

g <- g + edge("Lu", "Ch")
g <- g + edge("Lu", "Mic")

g <- g + edge("Ch", "Mic")

g <- g + edge("Da", "Co")
g <- g + edge("Da", "Ol")
g <- g + edge("Da", "En")
g <- g + edge("Da", "Gr")
g <- g + edge("Da", "Mil")

g <- g + edge("Co", "Ol")
g <- g + edge("Co", "En")
g <- g + edge("Co", "Gr")

g <- g + edge("Ol", "En")
g <- g + edge("Ol", "Mil")
g <- g + edge("Ol", "Gr")

g <- g + edge("En", "Gr")
g <- g + edge("En", "Mil")

g <- g + edge("Gr", "Mil")

g.adj <- as.matrix(get.adjacency(g))
g.net <- network(g.adj, directed = F)

```


### 18.  Compare your network to a random network and small world network of the same size (also set seed). Provide a brief description of network, including a table with the main descriptives and figures of degree distribution for all 3 networks. 

```{r, message=FALSE, warning=FALSE}
set.seed(1234)
# Generating a random graph 
rdm.matrix <- rgnm(1, 17, 53,mode="graph")
rdm.adjacency <- graph.adjacency(rdm.matrix)
rdm.edgelist <- get.edgelist(rdm.adjacency)

rdm.graph <- graph.data.frame(rdm.edgelist, directed = F)
rdm.net <- network(rdm.matrix, directed = F)

# Generating Small World Graph 
sm.graph <- watts.strogatz.game(dim=1, size=17, nei=3, p=0.1)

sm.adj <- as.matrix(get.adjacency(sm.graph))
sm.net <- network(sm.adj, directed = F)
```

```{r, echo = F, message=FALSE, warning=FALSE}
# Comparing main values of the three graphs 
# Average Path length 
av.path.g <- average.path.length(g, directed = F)
av.path.sm <- average.path.length(sm.graph, directed = F)
av.path.rdm  <- average.path.length(rdm.graph, directed = F)

av.paths <- c(av.path.g, av.path.sm, av.path.rdm)

# Betweenness 
bet.g <- betweenness(as.matrix(get.adjacency(g)))
bet.sm <- betweenness(as.matrix(get.adjacency(sm.graph)))
bet.rdm <- betweenness(as.matrix(get.adjacency(rdm.graph)))

betweenness <- as.data.frame(cbind(bet.g, bet.sm, bet.rdm))
colnames(betweenness) <- c("Own.Model", "Small.World", "Random.Model")

bet.means <- c(mean(bet.g,), mean(bet.sm), mean(bet.rdm))
bet.max <- c(max(bet.g), max(bet.sm), max(bet.rdm))

# Other descriptives 
node.numbers <- c(17, 17, 17)
edges.numbers <- c(53,51,53)
density <- c(gden(g.net, mode = "graph"), gden(sm.net, mode = "graph"), gden(rdm.net, mode = "graph"))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Creating boxplots for the betweenness 
library(tidyr)
betweenness <- gather(betweenness, model, betweenness, Own.Model:Random.Model, factor_key = T)

ggplot(betweenness)+
  geom_boxplot(aes(x = model, y = betweenness))+
  theme_bw()+
  labs(x = "Model",
       y = "Betweeness")

# Creating a table 
model.table <- cbind(node.numbers, edges.numbers, density, av.paths, bet.means, bet.max)

rownames(model.table) <- c("Own Modle", "Small World Model", "Random Model")
colnames(model.table) <- c("Nodes", "Edges", "Density", "Average Path", "Betweenness Average", "Betweeness Maximum")

kable(as.data.frame(model.table))
```
The created model has 17 nodes and 53 edges and therefor shows a density of 0.39. The nodes represent individual people and the the edges show regular contact (in person/phone call/messages). 
Due to the similar number of nodes and edges for my own and the random model and the close to similar numbers for the small world model, also the the density measure of all three models are more or less in line. More divergence can be seen in the centrality measures. While the random model and the small world model are relatively similar in terms of average path and average betweenness (with slightly higher numbers for the small world model), my own model shows much higher numbers. This illustrates the expected higher structuring of the model. This is further illustrates by the maximum betweenness level where my own model significantly exceeds the other two. This shows the much stronger centralization of the model on one (or a few actors). 



### 19.  Present a very basic visualisation of all 3 networks (just to capture the basic structure of connections). 

```{r, message=FALSE, warning=FALSE,  figures-side, fig.show="hold", out.width="50%"}
own_plot <- ggraph(g, layout="fr")+
  geom_edge_link(edge_colour="grey") +
  geom_node_point(
    aes(size = degree(g.net))) +
  theme_graph()+
  labs(size ="Degree")+
  ggtitle("Own Plot")

sm_plot <- ggraph(sm.graph, layout="fr")+
  geom_edge_link(edge_colour="grey") +
  geom_node_point(
    aes(size = degree(sm.net))) +
  theme_graph()+
  labs(size ="Degree")+
  ggtitle("Small World Plot")

rdm_plot <- ggraph(rdm.graph, layout="fr")+
  geom_edge_link(edge_colour="grey") +
  geom_node_point(
    aes(size = degree(rdm.net))) +
  theme_graph()+
  labs(size ="Degree")+
  ggtitle("Random Plot")

par(mar = c(1,3,.1,.1))
own_plot
sm_plot
rdm_plot

```
### 20.  Create a list of top 5 members by 3 centrality measures for your network. In your network: 



```{r, echo = F, message=FALSE, warning=FALSE}
# Creating a table with centrality measures 
deg.g <- degree(g.net)/2
clo.g <- closeness(g.net, gmode = "graph", cmode = "undirected")

cent.measures <- data.frame(V(g)$name, deg.g, clo.g, bet.g)
colnames(cent.measures) <- c("Name", "Degree", "Closeness", "Betweenness")

max.deg <- cent.measures %>%
  arrange(desc(Degree)) %>%
  filter(row_number() < 6) %>%
  select(Name, Degree)

max.clo <- cent.measures %>%
  arrange(desc(Closeness)) %>%
  filter(row_number() < 6) %>%
  select(Name, Closeness)

max.bet <- cent.measures %>%
  arrange(desc(Betweenness)) %>%
  filter(row_number() < 6) %>%
  select(Name, Betweenness)

max.cent.measures <- data.frame(max.deg, max.clo, max.bet)
colnames(max.cent.measures) <- c("Name(Degree)", "Degree", "Name(Closeness)", "Closeness", "Name(Betweeness)", "Betweenness")


kable(max.cent.measures)
```

Since the actor "He" shows the highest values in all three centrality measures, I would select this actor for both distributing information and as the person getting vaccinated first.

**a) Who you consider the key figure to contact for distributing information? Why?** 
For the information distribution (depending on if the aim is reaching everyone in the shortest time or as many people as possible directly), the closeness and degree measures might be more meaningful. The degree gives the direct contacts of a person, if it is high the information can directly pass the information to many people.The closeness parameter gives the closeness to all other actors. If it is high the actor is close to the other nodes and an inforamtion might therefor quickly reach everyone. 


**b) Who should get vaccinated first to avoid quick spreading of contagious disease? Why?** 
For deciding which person should be vaccinated first, the betweenness centrality might be more revealing, since the aim here is mainly to break infection chains for which an actor with high betweenness might be central. However, since the edges of the network do not measure personal interaction, but more a general regular contact that also includes phone calls and messages, the data is not very helpful to answer the question. 

###21.  Create a visualisation of your social network (use labels, colours etc)
```{r, echo = F, message=FALSE, warning=FALSE}
nodes.g <- data.frame(V(g)$name)
nodes.g$surname <- factor(c(1,1,2,1,2,3,4,3,5,3,3,6,1,6,6,6,6), labels= c("Covic", "Fütterer", "Kipp", "Kluge", "Maler", "Gedat"))

g_plot <- ggraph(g, layout="fr")+
  geom_edge_link(edge_colour="grey") +
  geom_node_point(
    aes(size = degree(g.net),
        color = nodes.g$surname)) +
  geom_node_text(aes(label=network.vertex.names(g.net)), 
                 size=2, repel=TRUE)+
  theme_graph()+
  labs(color ="Surname")

g_plot + guides(size = F)
```



